% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{csquotes}
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Chengyan Zhao}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge Chengyan Zhao }

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{}{8916-5 Takayama\\
  	Graduate School of Information Science\\
  	Nara Institute of Science and Technology \\
 Ikoma, Nara 630-0192, Japan \\}
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Tel: & (+81) 0743-72-5356 \\
    Email: & \href{mailto:zhao.chengyan.za5@is.naist.jp}{\tt zhao.chengyan.za5@is.naist.jp} \\
    Homepage: & \href{https://chengyanfox.github.io/}{\tt https://chengyanfox.github.io} \\
    Citizenship: &Chinese
  \end{tabular}
\end{minipage}

\section*{AREAS OF EXPERTISE}

\begin{itemize}
	\item Positive systems, Switched linear systems, Complex networks, Convex optimization, Deep learning.
\end{itemize}

\section*{EDUCATION}

\begin{itemize}
  \item Apr 2018- \hspace{6.9em}Ph.D. candidate in Information Science, \textit{Nara Institute of Science and Technology}
  \item Oct 2017-Mar 2018 \hspace{3em}Research student, \textit{University of Tokyo}
  
   \item Sep 2011-July 2013 \hspace{3em}M.Eng. in Control Engineer,  \textit{Northeastern University (China)}
   
  \item Sep 2007-July 2011 \hspace{3em}B.Eng. in Automatic Control,  \textit{Northeastern University (China)} 
\end{itemize}


\section*{AWARDS}

\begin{itemize}
\item Sep 2017-Mar 2021 \hspace{2.9em}Japanese Government (MEXT) Scholarships
\item Nov 2019 \hspace{7.0em}Overseas Dispatch Program (NAIST)
\end{itemize}

\section*{SHORT TERM VISITS}

\begin{itemize}
	\item Jan 2020-Feb 2020 \hspace{3.1em}Department of Mechanical Engineering, University of Hong Kong
	
\end{itemize}

\section*{PUBLICATIONS}

\subsection*{Journal Articles}

\begin{enumerate}[label={[\arabic*]}, noitemsep]
\item C. Zhao, M. Ogura, and K. Sugimoto, \enquote{Stability optimization of positive semi-Markov jump linear systems via convex optimization}, {\it SICE Journal of Control, Measurement, and System Integration, vol. 13, no. 5, pp. 233-239, 2020.}\\

\item W. Mei, C. Zhao, M. Ogura, and K. Sugimoto, \enquote{Mixed $H_2$/$H_{\infty}$ control for Markov jump linear systems with state and mode-observation delays}, {\it IET Control Theory and Applications, vol. 14, no. 15, pp. 2076-2083, 2020.}\\

\item C. Zhao, M. Ogura, M. Kishida, and A. Yassine, \enquote{Optimal resource allocation for dynamic product development process via convex optimization}, {\it Research in Engineering Design, 2020.}  \\

%\item C. Zhao, J. Xiao \enquote{Deep learning based state estimation of uncertain large-scale complex networks}, {\it Prepared for submission}.\\

%\item C. Zhao, M. Ogura, K. Sugimoto, \enquote{Log-log convexity of optimal control problem for positive linear systems}, Prepared for submission{\it }.
\end{enumerate}

\subsection*{Conference Proceedings}

\begin{enumerate}[label={[\arabic*]}, noitemsep]
\item L. Wang, C. Zhao, W. Cui, \enquote{Unmodeled dynamics and data-driven balance control for a class of underactuated mechanical systems,} {\it in Proceedings of the 2013 International Conference on Advanced Mechatronic Systems}, 2013, pp. 594-597.\\

\item C. Zhao, M. Ogura, K. Sugimoto, \enquote{Finite-time control of  discrete-time positive linear system via convex optimization,}  {\it SICE Annual Conference, 2020, Chiang Mai, Thailand (Online)}, pp. 1230-1235. 
\end{enumerate}

\section*{RESEARCH \& TEACHING SERVICE}
\begin{enumerate}[label={[\arabic*]}, noitemsep]
\item Sep 2018-\hspace{5.4em} Research Assistant.
\item Sep 2019-Feb 2020 \hspace{1.3em} Teaching Assistant (Japanese Culture).
\end{enumerate}

\section*{PROFESSIONAL SERVICE}
\textbf{Journal reviewer:} RAIRO - Operations Research; Journal of The Franklin Institute;


\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
   % \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
